---
title: "TEMPLATE"
author: "Steven Smith, PhD"
date: "MM/DD/YYY"
output: 
  html_document: 
    toc: yes
---

# TITLE
## BACKGROUND & APPROACH
A short snippet of the purpose of this markdown.
The following questions more or less become chunks below:
1. Question 1  
2. QUestion 2  

* Point 1  
* Point 2  

ASSUMPTIONS & LIMITATIONS: 

INPUT DATA LOCATION: 
OUTPUT DATA LOCATIOn: 

## PRE-ANALYSIS
The following sections are outside the scope of the 'analysis' but are still needed to prepare everything

### UPSTREAM PROCESSING/ANALYSIS
Process on a remote server
```{bash process_remote_server, eval=F}
# Typically code for processing data on a remote server. Used for tracability 

##------------------------------------------
# This denotes a subsection within the chunk
##------------------------------------------

##------------------------------------------

```

### SET UP ENVIORNMENT
Load libraries and set global variables
```{r setup, eval=F}

##------------------------------------------
## LIBRARIES
##------------------------------------------
library(ggplot2)
library(tidyverse)
library(plyr)
library(reshape2)
library(plot.utils)
##------------------------------------------

##------------------------------------------
# GLOBAL VARIABLES
##------------------------------------------
working_dir<-"/Users/stevensmith/Projects/" # don't forget trailing /
results_dir<-paste0(working_dir,"results") # assumes diretory exists
input_data1<-paste0(working_dir,"data/","data1.txt") 
input_data2<-paste0(working_dir,"data/","data2.txt") 
##------------------------------------------

```
### FUNCTIONS
List of functions
1. Function 1  
2. Function 2  
```{r functions, eval=F}
##------------------------------------------
## FUNCTION 1
##------------------------------------------
myfunction<-function(x){
  return(x+1)
}
##------------------------------------------
```

### READ IN DATA

```{r read_in_data, eval=F}

df1<-read.table(input_data1,sep="\t",header=T)
df2<-read.table(input_data2,sep="\t",header=T)

```

### PROCESS DATA
* This chunk handles transformations, data structure manipulations, summary stats.  
* However, try to keep the original data as unfiltered as possible (leave this for chunk-specific analysis).   
* The idea is to have eveyrthing each chunk needs at the ready.   
* If multiple chunks use the same filtered dataset, then filter in this chunk so that the same operation isn't being performed in multiple chunks.  
* Transformed dataframes should take the form "DF.TRANSFORMATION", .e.g, "input_data1.wide" if the new df is wide format.  
* Similarly, transformed columns should take the form 'COLNAME.TRANSFORMATION', e.g., "input_data1$col.log".  
* Summarized dataframes should take the form "DF.SUMMARY", .e.g, "input_data1.summary" like when computing summary statistics (condensing of original data).   

```{r process, eval=F}

##------------------------------------------
## ezample, log10 a column
##------------------------------------------
input_data1$col1.log10<-log(input_data1$col1,10)
##------------------------------------------

##------------------------------------------
## ezample, transform from long to wide
##------------------------------------------
input_data2.wide<-melt(input_data2)
##------------------------------------------

##------------------------------------------
## ezample, compute mean for col1
##------------------------------------------
input_data2.summary<-ddply(input_data2, c("col1"),summarise,col1.mean=mean(col1))
##------------------------------------------

```
## ANALYSIS
* This is the meat of the markdown where the heaviest lifting occurs and questions are answered.  
* This section should contain at least 1 chunk, up to about how many questions are to be addressed.  
* Keep processing of data light.  
* Try to map chunk names/headers to overall questions.
* Filtered data should take the form "DF.FILTERED", .e.g, "input_data1.filter".  
* Plot handles should take the form "DF.FILTERED.PLOT" .e.g, "input_data1.filter.plot".  

### QUESTION 1
A blurb about the approach, some context
```{r question1, eval=F}

##------------------------------------------
## filter input_data1
##------------------------------------------
input_data1.filter<-fitler(input_data1,col1=="foo")
##------------------------------------------

##------------------------------------------
## sub question 1
##------------------------------------------
table(input_data1.filter$col<5)
##------------------------------------------

##------------------------------------------
## sub question 2
##------------------------------------------
table(input_data1.filter$col<10)
##------------------------------------------

##------------------------------------------
## plot data
##------------------------------------------
(input_data1.filter.plot<-ggplot(input_data1.filter,aes(x=col1,y=col2.log))+
   geom_point()+
   default_plot_theme)
write_plot(input_data1.filter.plot,wd=results_dir)
##------------------------------------------

```
### QUESTION 2
Same format as question 1
```{r question2, eval=F}

##------------------------------------------
## filter input_data1
##------------------------------------------
input_data1.filter<-fitler(input_data1,col1=="foo")
##------------------------------------------

##------------------------------------------
## sub question 1
##------------------------------------------
table(input_data1.filter$col<5)
##------------------------------------------

##------------------------------------------
## sub question 2
##------------------------------------------
table(input_data1.filter$col<10)
##------------------------------------------

##------------------------------------------
## plot data
##------------------------------------------
(input_data1.filter.plot<-ggplot(input_data1.filter,aes(x=col1,y=col2.log))+
   geom_point()+
   default_plot_theme)
write_plot(input_data1.filter.plot,wd=results_dir)
##------------------------------------------

```
# CONCLUSION
A concluding remark(s) on the major findings, preferabbly to pointers where the data can be found. 

Helps to have a bullet point for each analysis chunk or an answer to each of the above 'questions':
*  Answer 1. 
*  Answer 2.  

#END
Cheatsheet:
http://rmarkdown.rstudio.com>
# TODO
* mkdir the results dir if it doesn't exist
* make ggplot a dependency for plot.utils?
